Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/compilation.tex
changes to failure description

In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable. We thus adopt a conservative analysis based on the observations above. The high-level idea is to order each PGIR node according to a \textit{can prefer} relation. For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around. Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures. Formally this means that $N_1$ can be preferred to $N_2$ when:
%
$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
%
where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
there is always a path to each ending location whenever this is a path from $N_2$ restricted to $G_i$.

>>>>

In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable. We thus adopt a conservative analysis based on the observations above. The high-level idea is to order each PGIR node according to a \textit{can prefer} relation. For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around. Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures. Formally this means that $N_1$ can be preferred to $N_2$ when:
%
$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
%
where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
there is always a path to each each ending location whenever this is a path from $N_2$ restricted to $G_i$.
